\documentclass{homework}
\class{BIT2008A/ITEC2000A: Multimedia Data Management}
\author{}
\date{Fall 2022}
\title{Lab 2}

\graphicspath{{./pics/}}

\begin{document} \maketitle

\section{SQL Basic Queries}
\begin{enumerate}
    \item Create two tables with names emp for employees and dept for departments.
    \begin{itemize}
        \item dept(\underline{deptno}, dname)
        \item emp(\underline{eid}, ename, salary, deptno)
    \end{itemize}
Discuss what datatype to choose for each attribute.
\item You are provided with \textit{dept\_data.sql} and \textit{emp\_data.sql} scripts. Populate your tables using those files.
\item Write a script to show all the rows in \textit{emp} table.
\item Write a script to show 5 of the employees who get more than 100 as their salary.
\item Create another table for projects:
\begin{itemize}
    \item prj(\underline{pid}, pname)
\end{itemize}
Projects and employees have a many-to-many relationship. We want to keep track of employees who have an active role in projects using an intermediate table named \textit{prjmember}. What should the schema of the such table look like?
\item Insert these projects into \textit{prj}:
\begin{itemize}
    \item Project 'A' having employees 'manager', 'b', and 'o' involved.
    \item Project 'B' having employees 'a', 'b', 'c', and 'd' involved.
    \item Project 'C' having employees 'a', and, 'f' involved.
    \item Project 'D' having employees 'manager', 'f', 'h', 'i', and 'g' involved.
\end{itemize}
\item Change the name of project 'D' to 'E'.

\item Write a script to show a list of employee names with their department name.

\item Write a script to show a list of employee names who work in 'sales' or 'inventory' departments.

\item Write a script to show a list of department names without any employees.

\item Write a script to show the name, salary, and department number of the employees with the highest earnings in each department.

\item Write a script to show a list of project names with fewer than 4 employees involved.

\item Write a script to show the summation of salaries for the employees involved in project 'B'.

\item Write a script to show a list of project names with the average salary of the employees involved in them.
\end{enumerate}



% \question Write down sets in order of containment.

% We pretend that equivalence classes are just numbers.
% \[
% 	\C \supset \R \supset \Q \supset \Z \supset \N \supset
% 	\P \not\supset (\GF[7] = \modulo[7])  \supset \{\nil\}
% \]

% \question Find roots of $x^2- 8x = 9$.
% \begin{align*}
% goigre & & \\
% guioshfg s& & \\
% \end{align*}

% We proceed by factoring,
% \begin{align*}
% 	x^2- 8x - 9     & = 9-9         &  & \text{Subtract 9 on both sides.}         \\
% 	x^2- x + 9x - 9 & = 0           &  & \text{Breaking the middle term.}         \\
% 	(x - 1)(x + 9)  & = 0           &  & \text{Pulling out common } (x - 1).      \\
% 	x               & \in \{1, -9\} &  & f(x)g(x) = 0 \Ra f(x) = 0 \vee g(x) = 0. \\
% \end{align*}

% \fig{0.3}{diagram.jpg}{Cipher wheels.}{wheel}

% \question Figure \ref{wheel} shows two cipher wheels. The left one is from Jeffrey Hoffstein, et al. \cite{hoffstein2008introduction} (pg. 3). Write a Python 3 program that uses it to encrypt: \texttt{FOUR SCORE AND SEVEN YEARS AGO}.

% \lstinputlisting[language=Python, caption={Python 3 implementing figure \ref{wheel} left wheel.}, label=gcd]{code/prog.py}

% We get: \texttt{KTZW XHTWJ FSI XJAJS DJFWX FLT}.

% % citations
% \bibliographystyle{plain}
% \bibliography{citations}

\end{document}